География названий юридических фирм в России

### 2024-09-05 law-firms-names/conference-paper/Conference-slides.qmd
Adjust paths, #4

# load the data
data <- read_csv(here("../../ru-smb-companies/legal/panel.csv"))
cluster_labels <- read_csv(
  here("conference-paper", "cluster-labels-conf.csv"))
vectors <- read_csv(here("common", "names-vectors.csv"))
ru <- st_read(here("common", "ru.geojson"))

>>>>

# load the data
data <- read_csv(here("common", "panel.csv"))
cluster_labels <- read_csv(
  here("conference-paper", "cluster-labels-conf.csv"))
vectors <- read_csv(here("common", "names-vectors.csv"))
ru <- st_read(here("common", "ru.geojson"))
